Hypertension and microbiome

### 2019-06-07 articletwo.Rmd
data frame can not be edited there

```{r pcoa plot}
pcoa.vectors <- pcoa.ordinate$vectors %>% as.data.frame
eig.fracs <- pcoa.ordinate$values$Relative_eig
pcoa.df <- merge(pcoa.vectors %>% select(Axis.1, Axis.2, Axis.3),
                 meta(pseq.species), by=0, all = TRUE) %>%
    mutate(STATETREATMENT = factor(paste0(HYPERTENSION, ANYDRUG),
                                   levels = c("11", "10", "01", "00")),
           gMAP = cut(oMAP, seq(60, 160, 15))) %>%
    gather(key, Axis, Axis.2, Axis.3)

@@

pcoa.plot <- ggplot(data=pcoa.df, aes(x=Axis.1, y=Axis, color = HYPERTENSION)) +
    facet_wrap(~key, labeller = axis_labeller) +
    geom_point(size=0.1, alpha=0.4) +
    xlab(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1])) +
    ylab(sprintf("Subsequent PCoA Axes", 100*eig.fracs[3])) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Normotensive", "Hypertensive"),
                        breaks=c(0, 1),
                        values = c("blue", "red")) +   
    coord_fixed() +
    scale_x_continuous(breaks=seq(-1, 1, .25)) +
    scale_y_continuous(breaks=seq(-1, 1, .25)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4))) +
    theme(text = element_text(size=14),
          legend.position = "none",
          strip.background = element_blank(),
          strip.placement = "outside")

>>>>

```{r pcoa plot}
pcoa.vectors <- pcoa.ordinate$vectors %>% as.data.frame
eig.fracs <- pcoa.ordinate$values$Relative_eig

pcoa.df <- merge(pcoa.vectors %>% select(Axis.1, Axis.2, Axis.3),
                 meta(pseq.species), by=0, all = TRUE) %>%
    mutate(STATETREATMENT = factor(paste0(HYPERTENSION, ANYDRUG),
                                   levels = c("11", "10", "01", "00")),
           gMAP = cut(oMAP, seq(60, 160, 15)))

@@

pcoa.plot <- ggplot(data=pcoa.df %>% gather(key, Axis, Axis.2, Axis.3),
                    aes(x=Axis.1, y=Axis, color = HYPERTENSION)) +
    facet_wrap(~key, labeller = axis_labeller) +
    geom_point(size=0.1, alpha=0.4) +
    xlab(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1])) +
    ylab(sprintf("Subsequent PCoA Axes", 100*eig.fracs[3])) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Normotensive", "Hypertensive"),
                        breaks=c(0, 1),
                        values = c("blue", "red")) +   
    coord_fixed() +
    scale_x_continuous(breaks=seq(-1, 1, .25)) +
    scale_y_continuous(breaks=seq(-1, 1, .25)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4))) +
    theme(text = element_text(size=14),
          legend.position = "none",
          strip.background = element_blank(),
          strip.placement = "outside")
